### 2019-04-09 initial/notes.tex
maybe?

>>>>

\subsection{Equation of Motion}

Consider Hamilton's equations applied to the Hamiltonian
\begin{align}
    \pd{\phi}{t} = -\pd{\mathcal{H}}{(\cos\theta)}
        &= -\cos\theta + \eta\p*{\cos I + \sin I \cot \theta \cos \phi},\\
    \pd{\theta}{t} = +\pd{\mathcal{H}}{\phi}
        &= -\eta \sin I \sin \theta \sin \phi.
\end{align}
This can be compared to the original EOM given in Kassandra's Eq.\ 12,
\begin{equation}
    \rd{\hat{s}}{t} =
        \p*{\hat{s} \cdot \hat{l}}\p*{\hat{s} \times \hat{l}}
            -\eta\p*{\hat{s} \times \hat{l}_p}.
\end{equation}
Recalling that $\abs*{\hat{\phi}} = \sin\theta$ (the differential geometry
result), we can verify the expressions are equivalent for $\phi = \pi$,
alignment with $\hat{s}, \hat{l}_p$ on the same side of $\hat{l}$ as in her
Fig.\ 2, checks our signs.
